A Study on Penguins: A Minimal Reproducible Example

### 2024-08-22 01_Example/Manuscript.qmd
Add table prefix (again)
Remove prefix again due to display issues and don't assume output format
See https://github.com/vincentarelbundock/tinytable/issues/327

```{r}
#| label: "tbl-descriptive-statistics"
#| echo: false
#| results: "asis"

# Call descriptive table with the vtable package
vtable::sumtable(data_clean, group = "species")

>>>>

```{r}
#| label: "descriptive-statistics"
#| echo: false
#| tbl-cap: "Summary Statistics"

modelsummary::datasummary_balance(formula = ~ species, data = data_clean, dinm = FALSE)
